A Guide to Pre-Processing High-Throughput Animal Tracking Data

### 2021-02-01 docs/ms_atlas_preproc_main_text_2021-02-01.tex
final edits before reformat

\documentclass[10pt,paper=a4]{scrartcl}
\usepackage{tgtermes}
\usepackage{helvet}
\usepackage{amsmath}
\usepackage[total={6.75in, 9.5in}]{geometry}
\setlength{\parindent}{2em}
% use Unicode characters - try changing the option if you run into troubles with special characters (e.g. umlauts)
\usepackage[utf8]{inputenc}

@@

% document begins here
\begin{document}
\vspace*{0.35in}

% title goes here:
\begin{flushleft}
{\Large
{\sffamily \textbf\newline{A Guide to Pre-Processing High-Throughput Animal Tracking Data}}
}
\newline
% authors go here:
\\
Pratik Rajan Gupte\textsuperscript{1, 2},
Christine E. Beardsworth\textsuperscript{2},
Orr Spiegel\textsuperscript{3},
Emmanuel Lourie\textsuperscript{4},
Sivan Toledo\textsuperscript{5},
Ran Nathan\textsuperscript{4},
Allert I. Bijleveld\textsuperscript{2}
% Author 4\textsuperscript{x},
% Author 5\textsuperscript{x},
% Author 6\textsuperscript{x},
% Author 7\textsuperscript{x}
\\
\bigskip
\textbf{1} Groningen Institute for Evolutionary Life Sciences, University of Groningen, The Netherlands.
\\
\textbf{2} Deptartment of Coastal Systems, NIOZ Royal Netherlands Institute for Sea Research, The Netherlands.
\\
\textbf{3} School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 69978, Israel.
\\
\textbf{4} Movement Ecology Lab, Department of Ecology, Evolution, and Behavior, Alexander Silberman Institute of Life Sciences, The Hebrew University of Jerusalem, 91904 Jerusalem, Israel.
\\
\textbf{5} Blavatnik School of Computer Science, Tel Aviv University, Israel.
\\
\bigskip

@@

PRG would like to thank Pedro M. Santos Neves for introducing PRG to \texttt{R} package development, for help with setting up \texttt{atlastools}, and for help with archiving it on Zenodo; 
A. Ramesh and F.J. Weissing for discussions on error propagation;
J.R.L. Gismann and E. Gobbens for feedback that improved the manuscript; 
members of the Modelling Adaptive Response Mechanisms Group (Weissing Lab), and the Theoretical Biology department at the University of Groningen for helpful discussions on \texttt{atlastools} and the manuscript.
All authors thank the attendees of ATLAS workshops held in May and June 2020 at the Hebrew University of Jerusalem for helpful comments on the pipeline and \texttt{atlastools}.

>>>>

\documentclass[10pt,paper=a4,headings=standardclasses
]{scrartcl}
\usepackage{mathpazo}
\usepackage{helvet}
\usepackage{amsmath}
\usepackage[total={6.75in, 9.5in}]{geometry}
\setlength{\parindent}{2em}
% use Unicode characters - try changing the option if you run into troubles with special characters (e.g. umlauts)
\usepackage[utf8]{inputenc}

@@

\title{A Guide to Pre-Processing High-Throughput Animal Tracking Data}
\date{}
\author{Pratik Rajan Gupte\textsuperscript{1, 2} \and 
Christine E. Beardsworth\textsuperscript{2} \and
Orr Spiegel\textsuperscript{3} \and
Emmanuel Lourie\textsuperscript{4} \and
Sivan Toledo\textsuperscript{5} \and
Ran Nathan\textsuperscript{4} \and
Allert I. Bijleveld\textsuperscript{2}}

% document begins here
\begin{document}
% \vspace*{0.35in}

% title goes here:
% {\Large
% {\sffamily \textbf\newline{A Guide to Pre-Processing High-Throughput Animal Tracking Data}}
% }
\maketitle

% \newline
% authors go here:

\begin{flushleft}
% Author 4\textsuperscript{x},
% Author 5\textsuperscript{x},
% Author 6\textsuperscript{x},
% Author 7\textsuperscript{x}
\bigskip
\textbf{1} Groningen Institute for Evolutionary Life Sciences, University of Groningen, The Netherlands.
\\
\textbf{2} Deptartment of Coastal Systems, NIOZ Royal Netherlands Institute for Sea Research, The Netherlands.
\\
\textbf{3} School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 69978, Israel.
\\
\textbf{4} Movement Ecology Lab, Department of Ecology, Evolution, and Behavior, Alexander Silberman Institute of Life Sciences, The Hebrew University of Jerusalem, 91904 Jerusalem, Israel.
\\
\textbf{5} Blavatnik School of Computer Science, Tel Aviv University, Israel.
\\
\bigskip

@@

PRG would like to thank Pedro M. Santos Neves for introducing PRG to \texttt{R} package development, for help with setting up \texttt{atlastools}, and for help with archiving it on Zenodo; 
Aparajitha Ramesh and Franjo Weissing for discussions on error propagation;
Geert Aarts, Jacob RL Gismann, Evy Gobbens for feedback that improved the manuscript; 
members of the Modelling Adaptive Response Mechanisms Group (Weissing Lab), and the Theoretical Biology department at the University of Groningen for helpful discussions on \texttt{atlastools} and the manuscript.
All authors thank the attendees of ATLAS workshops held in May and June 2020 at the Hebrew University of Jerusalem for helpful comments on the pipeline and \texttt{atlastools}.
